\bf A hierarchical failure-time model for heterogenous field data

### 2018-01-19 paper/m-lb-m-technometrics.tex
Clean up small typos.

\subsection{Model considerations}
Nonparametric methods require relatively few assumptions, but may not be suitable for prediction when extrapolation is required. Moreover, nonparametric estimates made using small samples, or data which are heavily censored may be too noisy to be useful. Appropriate parametric models can make better use of available data. For inference, likelihood-based methods are able to deal with truncated and/or censored data. Furthermore, by assuming a parsimonious representation of the data-generating process, parametric models admit simpler, more intuitive ways to compare sub-populations of interest, borrow strength across sub-populations, and incorporate prior information.

@@

\subsection{Overview}
The structure of the paper is as follows. Section~\ref{sec:Background} introduces the proposed method and potential applications and examines previous related work.  Section~\ref{sec:GLFP model} introduces the GLFP model and illustrates its use with a subset of hard drive failure data from the company, Backblaze.  In Section~\ref{sec:Data}, we describe the complete Backblaze Hard Drive data set, which is used throughout as a motivating example. In Section~\ref{sec:Hierarchical GLFP model} we discuss using hierarchical modeling of the GLFP model parameters to extend the GLFP model to multiple sub-populations. Section~\ref{sec:Data analysis} applies the hierarchical GLFP model to the hard drive data. First, we do model selection among four models of increasing complexity, using approximate leave-one-out cross-validation. Next, for the selected model, we assess the model fit using a graphical comparison of replicated data sets generated from the posterior distribution to the observed data. Finally, we present an evaluative comparison of sub-populations taking into account practical considerations related to product lifetime. Section~\ref{sec:Discussion} describes potential applications of our model and limitations for inference implied by the model assumptions.

@@

As discussed in Section \ref{sec:Weibull parameterization}, we reparameterize the Weibull distribution in terms of a quantile and the shape parameter because observed failure data are often more informative about the lower tail of their respective lifetime distribution (note that if $T$ has a Weibull distribution, $\sigma$ is a shape parameter for the distribution of $T$ and a scale parameter for the distribution of $\log(T)$). We truncate the distribution of $\sigma_{2g}$ at $1$ (indicated by $Tr(0,1)$ above) restricting the wearout failure mode to have an increasing hazard function (i.e., $\beta_{2g} = 1/\sigma_{2g}>1$). %We choose to model these parameters with log-normal and logit-normal distributions because many populations require strong regularization which the normal, with its exponentially decreasing tails, provides.

@@

Results showing the estimated elpd and associated standard errors for all 4 models are shown in Table \ref{table:2}.
We calculated the difference in expected predictive accuracy for Model 4 versus 3, Model 3 versus 2, and Model 2 versus 1, as well as the standard error of the difference (Table 1). For the models we considered, each successive increase in model complexity increases elpd.  Of all the models, Model 4 has significantly better elpd compared to the the other 3 models.

>>>>

\subsection{Model considerations}
Nonparametric methods require relatively few assumptions, but may not be suitable for prediction when extrapolation is required. Moreover, nonparametric estimates made using small samples or data which are heavily censored may be too noisy to be useful. Appropriate parametric models can make better use of available data. For inference, likelihood-based methods are able to deal with truncated and/or censored data. Furthermore, by assuming a parsimonious representation of the data-generating process, parametric models admit simpler, more intuitive ways to compare sub-populations of interest, borrow strength across sub-populations, and incorporate prior information.

@@

\subsection{Overview}
The structure of the paper is as follows. Section~\ref{sec:Background} introduces the proposed method, potential applications, and examines previous related work.  Section~\ref{sec:GLFP model} introduces the GLFP model and illustrates its use with a subset of hard drive failure data from the company, Backblaze.  In Section~\ref{sec:Data}, we describe the complete Backblaze Hard Drive data set, which is used throughout as a motivating example. In Section~\ref{sec:Hierarchical GLFP model} we discuss using hierarchical modeling of the GLFP model parameters to extend the GLFP model to multiple sub-populations. Section~\ref{sec:Data analysis} applies the hierarchical GLFP model to the hard drive data. First, we do model selection among four models of increasing complexity, using approximate leave-one-out cross-validation. Next, for the selected model, we assess the model fit using a graphical comparison of replicated data sets generated from the posterior distribution to the observed data. Finally, we present an evaluative comparison of sub-populations taking into account practical considerations related to product lifetime. Section~\ref{sec:Discussion} describes potential applications of our model and limitations for inference implied by the model assumptions.

@@

As discussed in Section \ref{sec:Weibull parameterization}, we reparameterize the Weibull distribution in terms of a quantile and the shape parameter because observed failure data are often more informative about the lower tail of their respective lifetime distribution (note that if $T$ has a Weibull distribution, $\sigma$ is a shape parameter for the distribution of $T$ and a scale parameter for the distribution of $\log(T)$). We truncate the distribution of $\sigma_{2g}$ at $1$ (indicated by $\text{Tr}(0,1)$ above) restricting the wearout failure mode to have an increasing hazard function (i.e., $\beta_{2g} = 1/\sigma_{2g}>1$). %We choose to model these parameters with log-normal and logit-normal distributions because many populations require strong regularization which the normal, with its exponentially decreasing tails, provides.

@@

Results showing the estimated elpd and associated standard errors for all 4 models are shown in Table \ref{table:2}.
We calculated the difference in expected predictive accuracy for Model 4 versus 3, Model 3 versus 2, and Model 2 versus 1, as well as the standard error of the difference (Table 2). For the models we considered, each successive increase in model complexity increases elpd.  Of all the models, Model 4 has significantly better elpd compared to the the other 3 models.
